---
title: "Averages"
author: "MAB"
date: '2022-03-02'
runtime: shiny 
editor_options: 
  chunk_output_type: console
output: 
  html_notebook 
---

```{r include=T, eval = F, tidy = T}

install.packages("renv", "readxl", "magrittr", "devtools", "dplyr")
renv::restore()
```

```{r include=T, eval = F, tidy = T}

knitr::opts_chunk$set(echo = TRUE)

#setwd("G:/Roberto-Angulo/script for average")

renv::autoload()
renv::activate()
```


```{r include=T, echo = T , eval = F, tidy = T}
#use this to save changes. Do not use when loading the project
renv::snapshot() 
```

## Averages between two .csv files.

In this code I will use two different directories(folder) that hold several .csv files. Those files have the same name in both directories but values inside each file where calculated differently.

I want to calculate the average between both files, column by column.

ex: Folder A, filesame.csv - Folder B, filesame.csv

::: {style="text-align:center"}
Exit file. Col 1= [(FolderA. filesame. col1) + (FolderB. filesame. col1)] /2
:::

::: {style="color:red; text-align:center"}
**Exit file Co1 - 2.5 = ( 2 + 3) /2**
:::

+-------------------------+---------+---------+
| Col1                    | Col2    | Col3    |
+:=======================:+:=======:+:=======:+
| ::: {style="color:red"} |         |         |
| [**2**]                 | 3       | 9       |
|{style="col:green"}:::|  |         |         |  +-------------------------+---------+---------+
| 5                       | 1       | 7       |
+-------------------------+---------+---------+
| 7                       | 4       | 2       |
+-------------------------+---------+---------+

: **FolderA-filesame**

+-------------------------+---------+---------+
| Col1                    | Col2    | Col3    |
+:=======================:+:=======:+:=======:+
| ::: {style="color:red"} |         |         |
| **3**                   | 4       | 8       |
| :::                     |         |         |
+-------------------------+---------+---------+
| 4                       | 2       | 8       |
+-------------------------+---------+---------+
| 8                       | 3       | 2       |
+-------------------------+---------+---------+

: **FolderB-filesame**

+-------------------------+---------+---------+
| Col1                    | Col2    | Col3    |
+:=======================:+:=======:+:=======:+
| ::: {style="color:red"} | 3.5     | 8.5     |
| **2.5**                 |         |         |
| :::                     |         |         |
+-------------------------+---------+---------+
| 4.5                     | 1.5     | 7.5     |
+-------------------------+---------+---------+
| 7.5                     | 3.5     | 2       |
+-------------------------+---------+---------+

: **Exit file from this code**

In case you want to check which packages are loaded run this line:

```{r include=T, echo = T , eval = F, tidy = T}
.packs= c("readxl", "magrittr", "devtools","dplyr")
lapply(.packs, require, character.only = TRUE)
```

Let's load our own functions that we defined in another file,

```{r include=T, echo = T , eval = F, tidy = T}
source("myfunciones.R")
```

Now, we need to locate the path to access the folders where the files are.

l = is the variable where we locate the path for the folder of files with landmarks obtained using FMNH 73441 (longirostrines) as template.

b = is the variable where we locate the path for the folder of files with landmarks obtained using UF 80928 (brevirostrines) as template.

```{r include=T, echo = T , eval = F, tidy = T}
l = "G:/Roberto-Angulo/Landmarks ALPACA server/FMNH73441 as template/spp average landmark"
b = "G:/Roberto-Angulo/Landmarks ALPACA server/UF80928 as template/spp average landmark"
```

The function "*prepare*" creates lists of the files contained in each of the folders, read the .csv files, and clean those files to be ready for further calculations.

```{r include=T, echo = T , eval = F, tidy = T}
prepare(l,b) 
```

Now we have two lists with the filenames. We need to check if those lists are equally long. This means that I have the same amount of files in each folder, if not, I need to check if I have missing files or extra files in one of the folders.

```{r include=T, echo = T , eval = F, tidy = T}
equalLong(ln, bn)

```

As folders contain the same amount of files we need to check that these folders contain the same file-names. The function "equalName" will check if file format is the same as well.

```{r include=T, echo = T , eval = F, tidy = T}
equalName(bn,ln)
```

The specimen name was collected from the file names and cleaned with the "nombreCol" function. Then we need to name columns with specimen name + coordinate(x, y, or z)

ex: 73683-84-x (first column-name); 73683-84y (second column-name), etc.

```{r include=T, echo = T , eval = F, tidy = T}
nombreCol(ln) 
xyzLn = paraCol
colnames(longClean)= xyzLn


nombreCol(bn)
xyzBn = paraCol
colnames(brevClean)= xyzBn
```

Now we need to calculate the average of each column for the two files that we prepared: **brevClean** and **longClean.**

```{r include=T, echo = T , eval = F, tidy = T}

averAges(brevClean,longClean)

colnames(misPromed) = stringr::str_replace_all(colnames(misPromed),c( "[.]" =  "-", "[X]" = ""))
```

Once the averages are calculated the obtained data frame will contain the averages for all files and its respective x,y,x coordinate. We need to split that data frame into several data frames so we can save each specimen and the 3 calculated coordinates averages in a single file (.csv). At the end we will get the same number of files that we had at the beginning in each folder. (in this case 87 files),

```{r include=T, echo = T , eval = F, tidy = T}

dfs <<- split.default(misPromed, gl(ncol(misPromed) / 3, 3))

names(dfs) = semiNames

path ="G:/Roberto-Angulo/Landmarks ALPACA server/land averages from temps/"

lapply(seq_along(dfs),function(i)(write.csv(dfs[[i]],file=paste0(path,names(dfs[i]),".fcsv"), row.names=FALSE)))
```
